The illusory promise of the Aligned Rank Transform

### 2025-05-31 text/20-background.qmd
starting new section

Another interesting finding of @luepsen:2018 was that the simple rank transformation *"appeared not as bad as it is often described"* [@luepsen:2018], outperforming ART in certain configurations, such as discrete and skewed distributions, or unequal variances. These results are in full contradiction with the findings of @Mansouri:1995.

>>>>

Another notable finding by @luepsen:2018 was that the simple rank transformation *"appeared not as bad as it is often described"* [@luepsen:2018], outperforming ART in many scenarios, such as discrete and skewed distributions, or distributions with unequal variances. These results are in full contradiction with the findings of @Mansouri:1995.
